\cvline{Name:}{Maksim~S.~Rakitin}
\cvline{Summary:}{I am a computational scientist at NSLS-II, BNL. I help
beamline staff and users run scientific experiments and perform data analysis. I
write code in Python to integrate hardware (motors, cameras, detectors,
\textit{etc.}) and 3rd-party software systems with the Bluesky data acquisition
framework. I am developing the Sirepo-Bluesky library that integrates Bluesky and
the Sirepo browser-based interface to scientific modeling codes to enable access
to ``virtual'' beamlines. I am a proponent of well-tested, modular, reusable,
sustainable, and easily accessible code. I am fluent with modern CI systems
(GitHub Actions, MS Azure Pipelines, \textit{etc.}) I use Docker/Podman
(including the creation of images), Linux (RHEL8, CentOS, Ubuntu,
\textit{etc.}), vagrant/VirtualBox on a daily basis. I am maintaining
\mylinkn{https://github.com/orgs/conda-forge/people?query=mrakitin}{over 100
conda-forge feedstocks} (Python, Python with C-extensions, C/C++, Fortran). I
lead the continuous integration efforts to deploy and test the conda
environments with the Bluesky software stack. I am enthusiastic about new
technologies and AI/ML projects. I am a PI on an AI/ML LDRD project and a PI for
two SBIR subcontracts with Radiasoft LLC (total funds of \$1M+).}

\cvline{News:}{Computer, Is My Experiment Finished?\newline
\mylink{https://www.bnl.gov/newsroom/news.php?a=220832}\newline\newline
Seeing the Forest Through the Trees: Brookhaven Lab Scientists
Develop New Computational Approach to Reduce Noise in X-ray Data\newline
\mylink{https://www.bnl.gov/newsroom/news.php?a=219533}}

\input{src/links}
