%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvline{2021.03--present
\href{https://www.bnl.gov/staff/mrakitin}{\logoBNL}
}
{\textbf{Associate Computational Scientist} and \textbf{Supervisor},
\textit{Data Science and Systems Integration (DSSI)
program, NSLS-II, Brookhaven National Laboratory},
Upton, NY (\mylink{https://www.bnl.gov}).
\newline
\textbf{Supervisor:} Dr.~Stuart Campbell}

\cvline{2019.10--2021.03
\href{https://www.bnl.gov/staff/mrakitin}{\logoBNL}
}
{\textbf{Associate Computational Scientist},
\textit{Data Acquisition, Management and Analysis (DAMA) group, NSLS-II,
Brookhaven National Laboratory},
Upton, NY (\mylink{https://www.bnl.gov}).
\newline
\textbf{Supervisor:} Dr.~Stuart Campbell}

\cvline{2017.11--2019.09
\href{https://www.bnl.gov/staff/mrakitin}{\logoBNL}
}
{\textbf{Assistant Computational Scientist},
\textit{Data Acquisition, Management and Analysis (DAMA) group, NSLS-II,
Brookhaven National Laboratory},
Upton, NY (\mylink{https://www.bnl.gov}).
\newline
\textbf{Supervisor:} Dr.~Stuart Campbell}

\textbf{Projects:}

\cvlistitem{\textbf{Bluesky} --- a library for experiment control and collection
of scientific data and metadata, \mylink{https://blueskyproject.io/bluesky}.}

\cvlistitem{\textbf{Ophyd} --- a device abstraction library,
\mylink{https://blueskyproject.io/ophyd}.}

\cvlistitem{\textbf{Databroker} --- a simple, user-friendly interface for
retrieving stored data and metadata from multiple sources,
\mylink{https://blueskyproject.io/databroker}.}

\cvlistitem{\textbf{Sirepo-Bluesky} --- an interface library between the
\textbf{Bluesky} data acquisition framework and the \textbf{Sirepo}
browser-based interface framework to beamline and accelerator simulation codes,
\mylink{https://github.com/NSLS-II/sirepo-bluesky}.}

\cvlistitem{Many other related software projects.}

\textbf{Responsibilities:}

\cvlistitem{Scientific software development \& maintenance.}

\cvlistitem{Packaging and maintenance of conda packages
(\texttt{conda-forge}, and formerly \texttt{lightsource2-tag} and
\texttt{nsls2forge} conda channels).}

\cvlistitem{Deployment of the software with Ansible.}

\cvlistitem{NSLS-II beamlines and users support.}

\cvlistitem{Active collaboration with peers at other US DOE National Labs (SLAC,
APS, ALS).}

\cvlistitem{Teaching people to use our software stack.}

\cvlistitem{Mentor to student interns (summer 2016 (1 intern), summer 2018 (1
intern), summer 2019 (1 intern), spring and summer 2020 (2 intern), summer 2021
(2 interns)).}

\vspace{0.3cm}
\hrule
\vspace{0.5cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvline{2015.12--2017.10
\href{https://www.bnl.gov/staff/mrakitin}{\logoBNL}
}
{\textbf{Research Associate (Postdoc)}, \textit{NSLS-II, Brookhaven National
Laboratory}, Upton, NY (\mylink{https://www.bnl.gov}).
\newline
\newline
\textbf{Supervisor:} Dr.~Oleg~Tchoubar (Chubar)}

\textbf{Projects:}

\cvlistitem{\textbf{Synchrotron Radiation Workshop (SRW)} --- computer code for
X-ray source and optics simulations, \mylink{https://github.com/ochubar/SRW}.}

\cvlistitem{\textbf{Sirepo} --- a cloud-based framework for SRW,
\mylink{https://github.com/radiasoft/sirepo}.}

\cvlistitem{\textbf{Image processing and data visualization},
\mylink{https://github.com/mrakitin/plotting} and
\mylink{https://github.com/mrakitin/experiments}.}

\cvlistitem{\textbf{CRL simulator} --- a code for simulation of a transfocator
(compound refractive lenses (CRL) for X-ray focusing),
\mylink{https://github.com/mrakitin/bnlcrl}.}

\vspace{0.2cm}
\textbf{Responsibilities:}

\cvlistitem{Adding new functionality to Sirepo (\emph{e.g.}, new optical
elements, new reports,
\mylinkn{https://github.com/radiasoft/sirepo/wiki/Dynamical-access-of-crystal-data-and-optical-constants-from-external-servers}{implementation}
of dynamical access of crystal data and optical constants from external
servers).}

\cvlistitem{Adding new functionality to SRW (\emph{e.g.}, new optical
elements).}

\cvlistitem{Creation of new SRW/Sirepo ``virtual beamline'' scripts/examples.}

\cvlistitem{Creation and update of
\mylinkn{https://github.com/radiasoft/sirepo/wiki}{Sirepo} \&
\mylinkn{https://github.com/mrakitin/SRW/wiki}{SRW} wiki documentation.}

\cvlistitem{SRW \& Sirepo users community support via GitHub issues, email
communication, \emph{etc.}}

\cvlistitem{Deployment of SRW \& Sirepo to NSLS-II servers for usage by beamline
scientists.}

\cvlistitem{Computational support for NSLS-II beamlines --- carrying out
required SRW \& Sirepo simulations.}

\cvlistitem{Assistance with scan plans preparation using \textbf{Bluesky} data
collection framework and \textbf{ophyd} package for controlling motors,
detectors, \emph{etc.}}

\cvlistitem{Participation in X-ray experiments (SRX, ESM, SMI, CHX beamlines of
NSLS-II) --- carrying out measurements and bulk data analysis, processing \&
visualization using Python (NumPy, SciPy, Matplotlib, PIL, \emph{etc.}; raw
data and images, NumPy arrays, HDF5 datasets).}

\cvlistitem{Implementation and integration of samples simulation code for
coherent scattering experiments in SRW and Sirepo (collaborative project with
CFN).}

\cvlistitem{Assisting with development of the Hartmann mask optical element in
SRW and its implementation in Sirepo (collaborative project with the Metrology
group of NSLS-II).}

\cvlistitem{Tutorship of summer students.}

\vspace{0.3cm}
\hrule
\vspace{0.3cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvline{2013.10--2015.12
\href{https://stonybrook.edu}{\logoSBU}
\href{https://uspex-team.org/en/uspex}{\logoUSPEX}
}
{\textbf{Postdoctoral Associate (Postdoc)}, \textit{Prof. Oganov's lab,
Department of Geosciences, Stony Brook University}, Stony Brook, NY
(\mylink{https://stonybrook.edu}, \mylink{https://uspex-team.org/en/uspex}).
\newline
\newline
\textbf{Supervisor:} Prof.~Artem~R.~Oganov}

\textbf{Projects:}

\cvlistitem{Refactoring of
\mylinkn{https://uspex-team.org/en/uspex}{USPEX} code and porting it from
Matlab to Python using modern programming techniques.}

\cvlistitem{\emph{Ab initio} investigation of BeF$_{2}$ and SiO$_{2}$ systems in
a wide pressures range
(\mylinkn{https://dx.doi.org/10.1039/C5CP04010H}{paper}) using
\mylinkn{https://uspex-team.org/en/uspex}{USPEX},
\mylinkn{http://vasp.at}{VASP},
\mylinkn{http://www.quantum-espresso.org}{Quantum Espresso},
\mylinkn{http://atztogo.github.io/phonopy/}{Phonopy}.}

\cvlistitem{Prediction of secondary structures of proteins from knowledge of
sequences of amino acids. Development of USPEX interface for
\mylinkn{http://dasher.wustl.edu/tinker/}{Tinker}.}

\vspace{1.0cm}
\textbf{Responsibilities:}

\cvlistitem{Main developer of the project on rewriting
\mylinkn{https://uspex-team.org/en/uspex}{USPEX} in Python with use of
NumPy, SciPy, TkInter, \emph{etc}. Web-based API creation.}

\cvlistitem{New
\mylinkn{https://uspex-team.org/en/uspex/release}{releases}
of Matlab/Octave version (USPEX 9.4.1, 9.4.2, 9.4.3, 9.4.4), new features, bug
fixes, maintenance.}

\cvlistitem{Development and maintenance of USPEX continuous integration system
(\mylinkn{http://han.ess.sunysb.edu/~testing/}{automatic nightly builds +
testing}).}

\cvlistitem{Development of tests for USPEX interface with VASP, GULP, LAMMPS,
CASTEP, Quantum Espresso, SIESTA, CP2K, QuantumWise ATK, DMACRYS, Tinker,
FHI-aims.}

\cvlistitem{Development and maintenance of online utilities
\mylink{http://han.ess.sunysb.edu} and
\mylinkn{https://uspex-team.org/en/uspex/tools}{https://uspex-team.org} using
JavaScript, jQuery, PHP, HTML, JSON, REST API, WebGL, XML, SVN, interfaces to
Python, Fortran, Matlab programs, \emph{etc.}}

\cvlistitem{Installation, configuration, and maintenance of
\mylinkn{http://qsh.ess.sunysb.edu:8000/trac}{Trac} system and SVN.}

\cvlistitem{Creation and maintenance of
\mylinkn{http://han.ess.sunysb.edu/uspex_manual}{USPEX manual} in \LaTeX, PDF,
HTML formats.}

\cvlistitem{\mylinkn{https://groups.google.com/forum/\#!forum/uspex} {USPEX
community} support.}

\vspace{0.3cm}
\hrule
\vspace{0.3cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvline{2008.10--2013.09
\href{https://www.susu.ru/en}{\logoSUSU}
}
{\textbf{Researcher}, \textit{Department of General and Theoretical Physics,
South Ural State University}, Chelyabinsk, Russia (\mylink{https://susu.ac.ru}).
\newline
\newline
\textbf{Supervisor:} Prof.~Alexander~A.~Mirzoev}

\textbf{Projects:}

\cvlistitem{Performing research on investigating influence of hydrogen on
structure and properties of iron-based alloys using DFT methods
(\mylinkn{http://www.wien2k.at}{WIEN2k}).}

\vspace{0.2cm}
\textbf{Responsibilities:}

\cvlistitem{Development of bash/Python utilities for monitoring WIEN2k
calculations in PBS/Torque and SLURM queues and for processing data of
calculations, developing mail notification system for the calculations.}

\cvlistitem{Installation of WIEN2k on a PC and on the university supercomputers
(SKIF Ural, SKIF Aurora, Tornado).}

\cvlistitem{Teaching and consulting students how to use WIEN2k both on a PC
and on supercomputers.}

\vspace{0.3cm}
\hrule
\vspace{0.3cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvline{2007.06--2013.10
\href{http://www.appliedtech.ru}{\logoAT}
\href{https://www.rocketsoftware.com}{\logoRocket}
}
{\textbf{QA Engineer, QA Team Leader}, \textit{Applied Technologies Ltd.},
Chelyabinsk, Russia (\mylink{http://www.appliedtech.ru}), a partner of Rocket
Software Inc., USA (\mylink{https://www.rocketsoftware.com})
\newline
\newline
\textbf{Supervisor:} Valery Ermakov, CEO}

\textbf{Projects:}

\cvlistitem{Tivoli Enterprise Portal (TEP) (August 2011 -- October 2013) --- QA
team leader. Responsibilities: software testing on Windows, Linux, Linux on z,
z/OS operating systems, GUI testing automation using
\mylinkn{https://www.ibm.com/us-en/marketplace/rational-functional-tester}{IBM
Rational Functional Tester}, creation of TEP Automated Testing System (TATS)
for automatic data verification using Python, REST API, JSON, XML, PHP, HTML,
JavaScript, jQuery in six TEP-enabled products:
\begin{itemize}
  \item[--]
  \mylinkn{http://www-03.ibm.com/software/products/en/ibmtivoadvarepoandmanafordfsm}
  {Tivoli Advanced Reporting and Management for DFSMShsm};
  \item[--]
  \mylinkn{http://www-03.ibm.com/software/products/en/tivoadvaaudifordfsm}
  {Tivoli Advanced Audit for DFSMShsm};
  \item[--]
  \mylinkn{http://www-03.ibm.com/software/products/en/advancedcatalogmanagementforzos}
  {Tivoli Advanced Catalog Management for z/OS};
  \item[--]
  \mylinkn{http://www-03.ibm.com/software/products/en/advancedbackupandrecoveryforzos}
  {Tivoli Advanced Backup and Recovery for z/OS};
  \item[--]
  \mylinkn{http://www-03.ibm.com/software/products/en/tivoadvaallomana}
  {Tivoli Advanced Allocation Management};
  \item[--]
  \mylinkn{http://www-03.ibm.com/software/products/en/automated-tape-alloc-mgr-zos}
  {Tivoli Automated Tape Allocation Manager for z/OS}.
\end{itemize}
Regular voice and video conversations with colleagues from the US.
}

\vspace{0.5cm}

\cvlistitem{\mylinkn{http://www-03.ibm.com/software/products/en/tivostormanaforzosmedi}
{Tivoli Storage Manager for z/OS Media} (February 2011 -- August 2011) --- QA
engineer. Responsibilities: software testing on Windows, Linux on z, Solaris,
AIX, z/OS operating systems with IBM DB2 databases, testing automation using
IBM-developed tools, bash, batch.}

\vspace{0.5cm}

\cvlistitem{\mylinkn{http://www-03.ibm.com/software/products/en/tivoadvaallomana}
{IBM Tivoli Advanced Allocation Management} (January 2009 -- January 2011) ---
QA engineer. Responsibilities: software testing on z/OS, testing automation
using bash, JCL, REXX. Regular voice and video conversations with colleagues
from the US.}

\vspace{0.5cm}

\cvlistitem{\mylinkn{http://www.rocketsoftware.com/products/rocket-servergraph}
{Rocket Servergraph Data Protection Expert} (June 2007 -- December 2008) --- QA
engineer. Responsibilities: software testing on Windows, Linux, Solaris, HP-UX,
AIX operating systems with PostgreSQL databases, GUI testing automation using
AutoIt3, automation of data verification using Perl and SQL. Regular voice and
video conversations with colleagues from the US.}

\vspace{0.3cm}
\hrule
\vspace{0.3cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvline{2006--2007
\href{https://www.susu.ru/en}{\logoSUSU}
}
{\textbf{System administrator}, \textit{Department of General and Theoretical
Physics, South Ural State University}, Chelyabinsk, Russia
(\mylink{https://susu.ac.ru}) \newline
Administer, secure and support Windows and Linux systems. Support HTTP server
(Apache), proxy server (Squid). Help others to troubleshoot operating system,
software, hardware and other issues. Also support the testing system for
students.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
